\chapter{Conclusion}
\label{conclusion}

In this thesis, we have reviewed the concept of "life-cycle investment" and summarized the common models and heuristics. We have presented our model as an application of Munk's (2016) recent findings and Olear's (2016) simulation techniques into Turkish retirement market.

\paragraph{}We have collected historical data to calibrate and estimate the best parameters to be used in our simulation. Using these parameters, we have constructed heterogeneous agents, who worked and invested throughout their lifetime. We considered different investment models that our hypothetical agents would use and calculated the resulting investment capitals. Finally, we have calculated and compared the welfare effects of all popular models to the individualized Munk's solutions.

\paragraph{}We have concluded that for rich-to-middle class risk-loving citizens, the individiualized strategies considerably increase their welfare. Moreover, the solutions we proposed can be solved analytically without complex dynamic optimizations, and therefore are easy to interpret to households.

\paragraph{}We also found that even naive life-cycle investment heuristics perform better than fixed lifetime investments. Our simulation showed that for risk-averse individuals with volatile wages, it is best to invest in housing in a proportion proposed by Munk.

\paragraph{}We propose these models to Turkish pension providers and to Turkish working-age households belonging to middle-to-upper class, as these options will increase their retirement welfare considerably.

