\chapter*{References}
\addcontentsline{toc}{chapter}{REFERENCES}

\begingroup
\renewcommand{\chapter}[2]{}
\begin{thebibliography}{}
\bibitem[Aktug et al.(2017)]{aktug} Aktuğ, E., Kuzubaş, T.U., Torul, O. (2017). An investigation of labor income profiles in Turkey. \textit{Working Papers, Boğaziçi  University, Department of Economics}.
\bibitem[Ascheberg et al.(2013)]{ascheberg} Ascheberg, M., Kraft, H., Munk, C., Weiss, F. (2013). The joint dynamics of labor income, stock prices, and house prices and the implications for household decisions. \textit{Working Papers, Dauphine Universite Paris, International Workshop on Pension, Insurance and Saving}.
\bibitem[Ben-Porath(1967)]{benporath} Ben-Porath, Y. (1967). The production  of  human  capital  and  the  life-cycle  of  earnings. \textit{Journal of Political Economy}, 75, 352-365.
\bibitem[Bodie et al.(1992)]{bodie}Bodie, Z., Merton, R.C., Samuelson, W.F. (1992). Labor supply flexibility and portfolio choice in a life-cycle model. \textit{Journal of Economic Dynamics and Control}, 16(3-4), 427-449. 
\bibitem[Campbell et al.(1999)]{ccgm} Campbell, J., Cocco, J.F., Gomes, F.J., Maenhout, P.J. (1999). Investing retirement wealth: A life-cycle model. \textit{Working Papers, National Bureau of Economic Research}, 439-482.
\bibitem[Canner et al.(1994)]{canner} Canner, N., Mankiw, N.G., Weil, D.N. (1997). An asset allocation puzzle. \textit{The American Economic Review}, 87(1), 181-191.
\bibitem[Chang et al.(2014)]{chang} Chang, Y., Hong, J.H., Karabarbounis, M. (2014). Labor-market uncertainty and portfolio choice puzzles. \textit{Working Papers, Federal Reserve Bank of Richmond}, 14(13).
\bibitem[Cocco et al.(2005)]{cgm} Cocco, J.F., Gomes, F.J., Maenhout P.J. (2005). Consumption and portfolio choice over the life cycle. \textit{The Review of Financial Studies}, 18(2), 491-533. 
\bibitem[Cocco(2004)]{cocco} Cocco, J.F. (2004). Portfolio choice in the presence of housing. \textit{The Review of Financial Studies}, 18(2), 537-567.
\bibitem[Flavin and Yamashita(2002)]{flavin} Flavin M., Yamashita T. (2002). Owner-occupied housing and the composition of the household portfolio. \textit{The American Economic Review}, 1, 345-362.
\bibitem[Markowitz(1952)]{markowitz} Markowitz H. (1952). Portfolio selection. \textit{The Journal of Finance}, 7(1), 77-91.
\bibitem[Merton(1971)]{merton} Merton R.C. (1971). Optimum consumption and portfolio rules in a continuous-time model. \textit{Journal of Economic Theory}, 3, 373-413.
\bibitem[Munk(2016)]{munk} Munk C. (2016). A mean-variance benchmark for household portfolios over the life cycle. \textit{Working Papers, Copenhagen Business School, Department of Finance}.
\bibitem[OECD(2018)]{oecd} OECD(2018). Long-term interest rates forecast (indicator). \textit{https://data.oecd.org}
\bibitem[Olear(2016)]{olear} Olear G.M. (2016). Benefits of individualized lifecycle investing: The impact of individual wage profile \& housing wealth. \textit{Master's Thesis, Tilburg University, School of Economics and Management}.
\bibitem[Samuelson(1969)]{samuelson} Samuelson, Paul A. (1969). Lifetime portfolio selection by dynamic stochastic programming. \textit{Review of Economics and Statistics}, 51(3), 239-246.
\bibitem[Tobin(1958)]{tobin} Tobin J.(1958). Liquidity preference as behavior towards risk. \textit{The Review of Economic Studies}, 25(2), 65-86.
\bibitem[Torul and Oztunali(2018)]{torul} Torul, O., Öztunalı, O. (2018). On income and wealth inequality in Turkey. \textit{Working Papers, Boğaziçi University, Department of Economics}.
\bibitem[Turkish Central Bank's Inflation Report (2018)]{tcmb} TCMB (2018). Enflasyon raporu. \textit{http://www.tcmb.gov.tr}.
\bibitem[Turkish Statistical Institute's Household Budget Survey(2003-2014)]{tuik} TUIK (2003-2014). Hanehalki butce anketi. \textit{Turkish Statistical Institute}.
\bibitem[Turkish Statistical Institute's Data Bank(2018)]{tuik2} TUIK (2018). General statistics. \textit{http://www.turkstat.gov.tr}.
\end{thebibliography}
\endgroup
