\chapter*{References}
\addcontentsline{toc}{chapter}{REFERENCES}

\begingroup
\singlespace
\begin{description}
\item Aktug, E., Kuzubas, T.U., Torul, O. (2017). An Investigation of Labor Income Profiles in Turkey. \textit{Working Papers, Bogazici University, Department of Economics}.
\item Arts, J., Ponds, E. (2016). The Need for Flexible Take-ups of Home Equity and Pension Wealth in Retirement. \textit{Working Papers, Tilburg University}.
\item Ascheberg, M., Kraft, H., Munk, C., Weiss, F. (2013). The Joint Dynamics of Labor Income, Stock Prices, and House Prices and the Implications for Household Decisions. \textit{Working Papers, Dauphine Universite Paris, International Workshop on Pension, Insurance and Saving}.
\item Bodie, Z., Merton, R.C., Samuelson, W.F. (1992). Labor Supply Flexibility and Portfolio Choice in a Life-Cycle Model. \textit{Journal of Economic Dynamics and Control},16(3-4), 427-449. 
\item Campbell, J., Cocco, J.F., Gomes, F.J., Maenhout, P.J. (2001). Investing Retirement Wealth: A Life-Cycle Model. \textit{Working Papers, National Bureau of Economic Research}, 439-482.
\item Campbell, J.Y., Viceira, L.M. (2002). Strategic Asset Allocation: Portfolio Choice for Long-Term Investors. \textit{Oxford University Press}.
\item Cocco, J.F., Gomes, F.J., Maenhout P.J. (2005). Consumption and Portfolio Choice over the Life Cycle. \textit{The Review of Financial Studies}, 18(2), 491-533. 
\item Flavin M., Yamashita T. (2002). Owner-Occupied Housing and the Composition of the Household Portfolio. \textit{The American Economic Review}, 1, 345-362.
\item Iscanoglu-Cekic, A. (2016). An Optimal Turkish Private Pension Plan with a Guarantee Feature. \textit{MDPI Risks Journal}, 4(19).
\item Markowitz H. (1952). Portfolio Selection. \textit{The Journal of Finance}, 7(1), 77-91.
\item Merton R.C. (1971). Optimum Consumption and Portfolio Rules in a Continuous-Time Model. \textit{Journal of Economic Theory}, 3, 373-413.
\item Munk C. (2016). A Mean-Variance Benchmark for Household Portfolios over the Life Cycle. \textit{Working Papers, Copenhagen Business School, Department of Finance}.
\item OECD (2018). Long-term interest rates forecast (indicator). \textit{https://data.oecd.org}
\item Olear G.M. (2016). Benefits of Individualized Lifecycle Investing: The Impact of Individual Wage Profile \& Housing Wealth. \textit{Master's Thesis, Tilburg University, School of Economics and Management}.
\item Pension Monitoring Center Annual Report (2016). \textit{https://www.egm.org.tr}.
\item Samuelson, Paul A. (1969). Lifetime Portfolio Selection by Dynamic Stochastic Programming. \textit{Review of Economics and Statistics}, 51(3), 239-246.
\item Tobin J. (1958). Liquidity Preference as Behavior Towards Risk. \textit{The Review of Economic Studies}, 25(2), 65-86.
\item Torul, O., Oztunali, O. (2018). On Income and Wealth Inequality in Turkey. \textit{Working Papers, Bogazici University, Department of Economics}.
\item TUIK (2003-2014). Hanehalki Butce Anketi. \textit{Turkish Statistical Institute}.
\end{description}
\endgroup
